Supplementary Information

### 2015-08-25 manuscript/AC-reply-to-referees.tex

  \begin{refquote}

    L98-99. According to some experts (e.g. the landmark 2002 book by Burnham
    and Anderson) when models differ less than 2 units in AIC, they have the
    same support and fit. On what theoretical grounds do you motivate the
    choice to select the model with the lowest AIC as the best-fit model when
    models have $\delta$AIC\textless2? To what extent does this choice affect your
    conclusions?

  \end{refquote}

  \textbf{R:} We are also aware of the general consensus    that models where
  $\delta$AIC\textless2 are roughly equally well-supported. This is why our
  procedure (as stated in lines XX-XX) was to first consider the set of models
  where $\delta$AIC\textless2 and select the model with the fewest degrees of
  freedom. We chose the smallest model where $\delta$AIC\textless2 in order to
  avoid over-fitting the models. We only used AIC as a deciding factor where
  there were several models that shared the minimal degrees of freedom and all
  had $\delta$AIC\textless2.  In fact, this scenario did not occur for the
  models presented in the previous draft   (it does occur when the by-trophic-
  level models use counts of species rather than proportions), so we have simply
  removed the description of this step of our analysis from the main text. [[If we go with species counts, will need to describe what the differences are between the similar models]]

@@

    \smallskip

     For readers outside the field, please explain in more detail the
     difference between `original species' and `trophic species' in food webs.

  \end{refquote}

  \textbf{R:} We thank the reviewer for their concern that our manuscript
  should be accessible to as wide a variety of    researchers as possible, and
  have followed the reviewer's suggestions in several places in the manuscript.
  [[sent DBS a draft of the conceptual figure]]

  At lines XX-XX we have added parenthetical explanations of the original and 
  trophic-species versions of food webs.

    We therefore analysed both original (i.e., without aggregating any species) and
    trophic-species (i.e., after aggregating species with identical predators and
    prey) versions of the dataset;

@@

    \smallskip

    Please justify why you use the proportion of species within a trophic
    level and not the absolute number of species per trophic level; at a first
    glance, this would be more intuitive for me given the focus of the study
    on scaling relationships with species richness.

  \end{refquote}

  \textbf{R:} Following the Referee's suggestion, we have moved our analysis
  of scaling relationships by trophic levels to the supplemental information.
  We hope that this will address the Referee's first two concerns above. We thank the
  Referee for this suggestion as it has allowed us more space to describe our network
  measures in more accessible terms.

  In fact we did analyse absolute numbers of species within a trophic level as well 
  as proportions. Both ways of defining the distribution of species across trophic levels
  have benefits (absolute numbers are more intuitive, as the Referee points out, while
  proportions feature in more of the food-web literature) and so we ultimately decided
  on proportions because the trends were clearer than in absolute numbers. [[Should we just
  give both now that this is in the supplemental?]]

### 2015-08-27 manuscript/AC-reply-to-referees.tex

  \begin{refquote}

    L187-198. For your explanation why the scaling relationship changes with
    latitude in lake and stream food webs and not in the other ecosystem types
    to be convincing it is not enough to cite studies that high-latitude
    aquatic species tend to switch between different seasonally available
    prey, you also need to provide evidence from the literature that this is
    not the case in the other ecosystem types.

  \end{refquote}

  \textbf{R:} We do not think it likely that we will be able to find evidence that prey-
    switching does not occur in certain ecosystem types because, by definition,
    it is impossible to document an event that does not occur. In fact, there are almost
    certainly examples of species which switch between different prey in any ecosystem type
    at any latitude. As we do not feel qualified to conduct a review of the frequencies of
    prey-switching, we have instead revised our discussion following an excellent suggestion
    by Referee 1 to focus on the greater seasonality experienced by stream communities.
    [[not done, will need to tone this down.]]

  \begin{quotation}
  \end{quotation}

@@

  \textbf{R:} We have changed all refences to the Vancouver style and have 
    added sections for author contributions, conflicts of interest, and funding.
    [[Check the in-text citations match published papers]]

  \newpage

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Reviewer 1}
% ---------------------------------------

  The Reviewer was very positive about our manuscript, calling it
  ``an interesting paper that takes advantage of recent compilations
  of food webs to test basic theory with respect to latitudinal gradients in
  niche breadth'', ``exceptionally well written and presented'', ``sophisticated
  and well thought out''. We thank the Reviewer for their kind words,
  and also for their suggestions for further improving our manuscript. We
  have addressed each comment below (in italics), and are confident that our
  responses (preceded by a \textbf{R}) have further improved the manuscript.

@@

  \begin{refquote}

    My concern here is how much of the pattern can be attributed to true
    ecological effects – as opposed to the consequences of differences in the
    effort used to describe different food webs... It could be explored to some extent by
    analysing for an effect of particular authors (e.g. the Thompson and
    Townsend food webs which dominate the stream dataset) but ultimately there
    is every chance that the results here are artefacts of differences in
    sampling effort between studies. Might it be possible to randomise the
    datasets, excluding particular food webs (or authors) to determine
    robustness to this effect??

  \end{refquote}

  \textbf{R:} We share the reviewer's concern that variation in sampling
  effort could be driving the trends we observe, as it is highly likely that
  the authors of all 196 webs in our dataset did not follow the same procedures.
  Following the reviewer's suggestion, we have jackknifed our models by systematically
  removing each web in turn and then re-running our analysis. We then repeated this
  process, removing each author (or set of authors where authors worked on identical sets
  of food webs) in turn and re-fitting the models. We are happy to report that removing
  any single web had no significant effect on any model, nor did removing any author
  (we removed Thompson and Townsend separately as each worked on one web that the other
  did not). We have added a description of these methods and summary figures of their results
  to the supporting information, and we thank the reviewer for suggesting this validation
  of our overall results. [[done]] We have also added a brief note in the main text to direct other
  readers with similar concerns to the supporting information. [[not done]]

@@

  \end{quotation}

  \newpage

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Reviewer 2}
% ---------------------------------------

  Polite pre-amble.
  ``This is an interesting study on a timely and important topic. The core analysis of the paper (scaling relationships of food web metrics with species richness) are convincingly presented and comprehensively discussed.''1

### 2015-08-27 manuscript/supplement.tex

\vspace{0.4 in}
\beginsupplement
\linenumbers
% \begin{landscape}
\subsection*{Appendix S1: Details of Food Web Sources and Selection}

@@

\subsection*{Appendix S2: Forms of scaling Relationships with S}

@@

>>>>

\vspace{0.4 in}
\beginsupplement
\linenumbers
% \begin{landscape}
\subsection*{Appendix S1: Details of food web sources and selection}

@@

\subsection*{Appendix S2: Forms of scaling relationships with species richness}

@@

\subsection*{Appendix SX: Testing for effects of sampling effort}

  \subsubsection*{Methods}
    As our dataset consists of food webs published over several decades, from 
    many countries, and by many research groups, it is highly likely that not
    all webs were compiled using the same procedure or with the same degree of
    sampling effort. In order to insure that our results were not driven by
    particularly unusual food webs, or by unusually well- or poorly-sampled webs 
    derived from any particular group, we performed two jackknife tests of our 
    results. In the first test, we removed one web from our dataset and re-fit 
    our models, then repeated this process for all webs in the dataset. We then 
    plotted the estimates for each coefficient in each of our models in order to 
    determine whether the omission of any web dramatically changed the resulting 
    model. In the second test, we removed groups of webs assembled by a given 
    author (or authors, where two or more authors assembled identical sets of 
    food webs) and again plotted the resulting collection of estimates for each
    coefficient. We did not plot the coefficients resulting from the removal of
    authors who compiled a single food web, as these were included in the first
    test. This allowed us to determine whether the inclusion or exclusion
    of the webs assembled by a particular researcher or group of researchers
    affected our results.

    None of our models were affected by the removal of any single food web.
    Estimates of co-efficients from all jackknifed datasets were extremely
    similar (Figs.~\ref{LS_web,Gen_web,Vul_web}). Moreover, our models were also robust to the removal
    of any given author (Figs.~\ref{LS_auth,Gen_auth,Vul_auth}). We are therefore very confident that,
    while there are undoubtedly differences in the methods used to compile food webs,
    these differences are not driving the trends we report in this study.

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/LS_web.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across food webs. We show the estimates (+/- 1SE) of each coefficient
    in the equation after the removal of each web in the dataset. All estimates are colour
    coded according the ecosystem type of the removed web.}
    \label{LS_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Gen_web.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across food webs. We show the estimates (+/- 1SE) of each coefficient
    in the equation after the removal of each web in the dataset. All estimates are colour
    coded according the ecosystem type of the removed web.}
    \label{Gen_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Vul_web.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across food webs. We show the estimates (+/- 1SE) of each coefficient
    in the equation after the removal of each web in the dataset. All estimates are colour
    coded according the ecosystem type of the removed web.}
    \label{Vul_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/LS_author.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the estimates (+/- 1SE) of each coefficient
    in the equation after the removal of all webs compiled by each author in the dataset.}
    \label{LS_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Gen_author.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the estimates (+/- 1SE) of each coefficient
    in the equation after the removal of all webs compiled by each author in the dataset.}
    \label{Gen_web}
    \end{figure}

    \begin{figure}[h]
    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Vul_author.eps}}
    \caption{Estimates of the coefficients in equation XX do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the estimates (+/- 1SE) of each coefficient
    in the equation after the removal of all webs compiled by each author in the dataset.}
    \label{Vul_web}
    \end{figure}
